Datasheet for 'A dataset

### 2024-03-29 other/datasheet/datasheet_template.qmd
Move datasheet and add checklist to README

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references_datasheet.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Extract of the questions from @gebru2021datasheets

>>>>

---
title: "Datasheet for 'A dataset'"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.
